---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# velocimeter

<!-- badges: start -->
<!-- badges: end -->

The goal of velocimeter is to calculate terminal velocity using a physical model for free fall with air resistance.

## Installation

You can install the development version of velocimeter like so:

``` r
# install.packages("devtools")
# library(devtools)
# install_github("jinleizhu/velocimeter")
```

## Example

This is a basic example which shows you how to 1) convert image coordinates to
real coordinates in 3-d space, 2) calculate terminal velocity using the physical
model for free fall with air resistance, and 3) diagnose the measurements of
terminal velocity.

```{r example}
library(velocimeter)
# 1) convert image coordinates to real coordinates in 3-d space
datx <- read.csv(file = paste0(system.file(package = "velocimeter"),"/extdata/datx.csv"),header = TRUE)
xcalib(dat=datx)

# 2) calculate terminal velocity using the physical model for free fall with air resistance
# NOTE: When using the function, you should change the path to your .txt files.
calculate.terminal.velocity.phys(file = paste0(system.file(package = "velocimeter"),"/extdata/agri-short_00000.aviResults.txt"),
min.size = 10,min.circularity = 0.05,fps = 130,tubelength = 1.075)

# 3) diagnose the measurements of terminal velocity:
# NOTE: When using the function, you should change the path to your vtobj.Rdata file.
load(file = paste0(system.file(package = "velocimeter"),"/extdata/vtobj.Rdata"))
absdiff.veloc(obj = vtobj[[1]])
rmse.veloc(obj = vtobj[[1]])

```
