---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# velocimeter

<!-- badges: start -->
<!-- badges: end -->

The goal of velocimeter is to calculate terminal velocity using a physical model for free fall with air resistance.

## Installation

You can install the development version of velocimeter like so:

``` r
# 1. Code -> Download ZIP from GitHub repository (https://github.com/jinleizhu/velocimeter)
# 2. Unzip the file
# 3. Open velocimeter.Rproj in Rstudio
# 4. Prior to first testing, click the "Build" pane (upper right), and then "Install and Restart"

```

## Example

This is a basic example which shows you how to calculate terminal velocity using
the physical model for free fall with air resistance (shown in the "test.R" script):

```{r example}
library(velocimeter)
calculate.terminal.velocity.phys(file = "terminal_velocity_analysis20219191543/agri-short_00000.aviResults.txt",
                                 min.size = 10,min.circularity = 0.05,fps = 130,tubelength = 1.075)

```

